\documentclass[12pt]{article}
\usepackage{array}
\usepackage{ragged2e}
\usepackage[svgnames,table]{xcolor}
\color{gray}
\usepackage{longtable}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{hhline}
\usepackage{multicol}
\usepackage{lastpage}
\usepackage{multirow}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage[paperheight=11.0in,paperwidth=8.5in,top=1in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage[none]{hyphenat}
\usepackage{fontspec}
\setmainfont[AutoFakeSlant=0.3]{Rasa}

\hypersetup{colorlinks,allcolors=[HTML]{0B5394},pdfinfo={Title={Curriculum Vitae of Bryan Dosono},Author={Bryan Dosono},Creator={Bryan Dosono},Subject={Curriculum Vitae},Keywords={Curriculum Vitae},CreationDate={D:20181014232724}}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\pagestyle{fancy}
\fancyhf{}
\cfoot{
\vspace*{0in}
\textcolor{grey}{
\begin{tabular}{Rp{1.0in}p{0.2in}|p{4.8in}}
& {\footnotesize{\thepage/9}} & { \footnotesize{Dosono, CV}} \\
\end{tabular}}}

\renewcommand{\headrulewidth}{0pt}
\setlength{\topsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\renewcommand{\arraystretch}{1}
%\renewcommand{\baselinestretch}{1.1}
%\setlength\tabcolsep{0pt}

\definecolor{grey}{HTML}{3E3D3C}
\begin{document} 
{\RaggedRight {\color{grey}
\setlength \extrarowheight{5pt}
\begin{longtable}{Rp{1.0in}p{0.25in}p{4.75in}}

&& \Huge \textcolor{black}{\uppercase{Bryan Dosono}} \par \normalsize \href{mailto:info@bdosono.com}{{info@bdosono.com}} $\vcenter{\hbox{\tiny$\bullet$}}$ \href{http://www.bdosono.com/}{{www.bdosono.com}} \par Curriculum Vitae, June 2019
\\
\\
&& \par \Large \textcolor{black}{\uppercase{Education}} \\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Doctor of Philosophy}}} & \footnotesize{2019} & \href{https://ischool.syr.edu/bdosono}{{Ph.D. in Information Science and Technology}}
\par Syracuse University (SU), School of Information Studies, Syracuse, NY \par Concentration: Data Science \\ && \textcolor{black}{Research Areas}: Human-Computer Interaction, Computer-Supported Cooperative Work, Social Computing, Online Identity \\ && \textcolor{black}{Research Methods}: Interviews, Contextual Inquiry, Content Analysis, Exploratory Data Analysis, Focus Groups, Virtual Ethnography, Participatory Design, Card Sorting \\

\textcolor{black}{\footnotesize{\uppercase{Bachelor of Science}}} & \footnotesize{2013} & \href{https://web.archive.org/web/20140402144404/http://ischool.uw.edu/research/student-research/dosono}{{B.S. in Informatics: Human-Computer Interaction}} \par University of Washington (UW), Information School, Seattle, WA \par College Honors, Phi Beta Kappa, Magna Cum Laude, Minor: Music \\ && \textcolor{black}{Technical Skills}: Statistical Analysis (R), Object-Oriented Programming (Python, Java), Front-End Web Development (HTML, CSS, JavaScript), Databases (MySQL, MongoDB), Visualization (Tableau) \\ && \textcolor{black}{Design Skills}: Design (Photoshop, Illustrator), Motion Graphics (After Effects), Photography (Lightroom), Diagramming (Visio, Lucidchart), Wireframing (Figma, Balsamiq) 
\\
\\
&&\par \Large \textcolor{black}{\uppercase{Employment}}\\ \hhline{~~-} 

\textcolor{black}{\footnotesize{\uppercase{Academic}}} & \footnotesize{2017} & \href{http://bits.ischool.syr.edu/}{{Doctoral Researcher}}, Syracuse University \\ && \textcolor{black}{Research}: Behavior, Information, Technology and Society Laboratory (Research Assistant); Social Computing Systems Laboratory (Research Assistant) \\ && \textcolor{black}{Teaching}: Human-Computer Interaction (Guest Lecturer); Introduction to Asian American Studies (Guest Lecturer); Theories of Digital Technology (Teaching Assistant); Information Reporting and Presentation (Teaching Assistant); Social Web Technologies (Teaching Assistant) \\

& \footnotesize{2016} & \href{http://www.sis.pitt.edu/i3/phd-fellows/fellow-profiles.html}{{Teaching Fellow}}, University of Pittsburgh \\ &&\textcolor{black}{Research}: iSchool Inclusion Institute (Advisor) \\ &&\textcolor{black}{Teaching}: Python Programming (Instructor) \\

\textcolor{black}{\footnotesize{\uppercase{Industry}}} & \footnotesize{2018} & \href{https://www.airbnb.com/}{{Experience Research Ph.D. Intern}}, Airbnb \\

& \footnotesize{2018} & \href{https://vsfs.state.gov/about}{{Virtual Student Federal Service Research Intern}}, National Aeronautics and Space Administration \\

& \footnotesize{2013} & \href{https://www.google.com/policyfellowship/2013fellows.html}{{Google Policy Fellow}}, New America Foundation Open Technology Institute \\

& \footnotesize{2012} & \href{https://students.googleblog.com/2012/09/a-new-class-of-google-student.html}{{Brand Ambassador}}, Google \\

& \footnotesize{2008} & \href{https://www.engr.washington.edu/current/studentprogs/alva}{{Engineering Intern}}, Boeing Company
\\
\\
&&\par \Large \textcolor{black}{\uppercase{Research}} \\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Dissertation}}} & \footnotesize{[D1]} &  \href{https://ischool.syr.edu/events/view/dissertation-defense-bryan-dosono/}{{Dosono, B.}} (2019). Identity work of Asian Americans and Pacific Islanders on Reddit: Traversals of deliberation, moderation, and decolonization. \\

\textcolor{black}{\footnotesize{\uppercase{Peer-reviewed Journal Publications}}} & \footnotesize{[J3]} & \href{https://doi.org/10.1109/MIC.2018.112101619}{{Dosono, B.}}, Hayes, J., Wang, Y. (2018). Toward accessible authentication: Learning from people with visual impairments. \textit{IEEE Internet Computing}, 22(2). 62-70. \\

& \footnotesize{[J2]} & \href{https://dl.acm.org/authorize?N42807}{{Dosono, B.}}, Rashidi, Y., Akter, T., Semaan, B., Kapadia, A. (2017). Challenges in transitioning from civil to military culture: Hyper-selective disclosure through ICTs. \textit{Proceedings of the ACM on Human-Computer Interaction}, 1. 41:1-23 ACM. \\

& \footnotesize{[J1]} & Gomez, R., Pather, S., \href{https://doi.org/10.1002/j.1681-4835.2012.tb00366.x}{{Dosono, B.}} (2012). Public access computing in South Africa: Old lessons and new challenges. \textit{The Electronic Journal of Information Systems in Developing Countries}, 52(1). 1-16. \\

\textcolor{black}{\footnotesize{\uppercase{Peer-reviewed Conference Proceedings}}} & \footnotesize{[C14]} & \href{https://doi.org/10.1145/3290605.3300372}{{Dosono, B.}}, Semaan, B. (2019). Moderation practices as emotional labor in sustaining online communities: The case of AAPI identity work on Reddit. \textit{Proceedings of the 2019 CHI Conference on Human Factors in Computing Systems}. 142:1-142:13. ACM. \\

& \footnotesize{[C13]} & Grimaldi, V., Figueroa, J., Sullivan, J., \href{https://doi.org/10.1007/978-3-030-15742-5_29}{{Dosono, B.}} (2019). From gridiron gang to game plan: Impact of ICTs on student athlete information seeking practices, routines, and long-term goals. \textit{Information in Contemporary Society}. 290-301. Springer International Publishing. \\

& \footnotesize{[C12]} & \href{https://dl.acm.org/authorize?N658208}{{Dosono, B.}}, Semaan, B. (2018). Identity work as deliberation: AAPI political discourse in the 2016 US Presidential Election. \textit{Proceedings of the 2018 CHI Conference on Human Factors in Computing Systems}. 633:1-12. ACM. \\

& \footnotesize{[C11]} & Booth, K., \href{https://doi.org/10.1007/978-3-319-78105-1_75}{{Dosono, B.}}, Redmiles, E., Morales, M., Depew, M., Herman, E., Trahan, K., Tananis, C., Farzan, R. (2018). Diversifying the next generation of information scientists: Six years of implementation and outcomes for a year-long REU program. \textit{Transforming Digital Worlds}. 655-664. Springer International Publishing. \\

& \footnotesize{[C10]} & \href{https://dl.acm.org/authorize?N41342}{{Dosono, B.}}, Semaan, B., Hemsley, J. (2017). Exploring AAPI identity online: Political ideology as a factor affecting identity work on Reddit. \textit{Proceedings of the 2017 CHI Conference Extended Abstracts on Human Factors in Computing Systems}. 2528-2535. ACM. \\

& \footnotesize{[C9]} & Bratt, S., Semaan, B., Britton, L., \href{http://idl.iscram.org/show.php?record=1463}{{Dosono, B.}}, Franco, Z. (2017). Translation in personal crises: Opportunities for wearables design. \textit{Proceedings of the 14th International Conference on Information Systems for Crisis Response And Management}. 266-279. ISCRAM. \\

& \footnotesize{[C8]} & Hayes, J., \href{http://hdl.handle.net/2142/96755}{{Dosono, B.}}, Wang, Y. (2017). ``They should be convenient and strong'': Password perceptions and practices of visually impaired users. \textit{iConference 2017 Proceedings}. 445-451. \\

& \footnotesize{[C7]} & Semaan, B., \href{https://dl.acm.org/authorize?N41343}{{Dosono, B.}}, Britton, L. (2017). Impression management in high context societies: `Saving face' with ICT. \textit{Proceedings of the 2017 ACM Conference on Computer Supported Cooperative Work and Social Computing}. 712-725. ACM. \\

& \footnotesize{[C6]} & Semaan, B., Britton, L., \href{https://dl.acm.org/authorize?N41344}{{Dosono, B.}} (2017). Military masculinity and the travails of transitioning: Disclosure in social media. \textit{Proceedings of the 2017 ACM Conference on Computer Supported Cooperative Work and Social Computing}. 387-403. ACM. \\

& \footnotesize{[C5]} & Semaan, B., Britton, L., \href{https://dl.acm.org/authorize?N41455}{{Dosono, B.}} (2016). Transition resilience with ICTs: `Identity awareness' in veteran reintegration. \textit{Proceedings of the 2016 CHI Conference on Human Factors in Computing Systems}. 2882-2894. ACM. \\

& \footnotesize{[C4]} & \href{https://doi.org/10.9776/16285}{{Dosono, B.}} (2016). Patron privacy: A luxury concern for marginalized Internet users. \textit{iConference 2016 Proceedings}. \\

& \footnotesize{[C3]} & \href{https://www.usenix.org/conference/soups2015/proceedings/presentation/dosono}{{Dosono, B.}}, Hayes, J., Wang, Y. (2015). ``I'm stuck!'': A contextual inquiry of people with visual impairment in authentication. \textit{Symposium On Usable Privacy and Security}. 151-168. USENIX Association. \\

& \footnotesize{[C2]} & \href{https://doi.org/10.9776/14043}{{Dosono, B.}} (2014). Digital inclusion for migrant millennials: Improving the ICT landscape of Yakima Valley Schools. \textit{iConference 2014 Proceedings}. 65-75. \\

& \footnotesize{[C1]} & Ko, A., \href{https://dl.acm.org/authorize?N41457}{{Dosono, B.}}, Duriseti, N. (2014). Thirty years of software problems in the news. \textit{Proceedings of the 7th International Workshop on Cooperative and Human Aspects of Software Engineering}. (pp. 32-39). ACM. \\

\textcolor{black}{\footnotesize{\uppercase{Workshop Submissions}}} & \footnotesize{[W2]} & Akter, T., \href{https://chi2019.acm.org/accepted-workshops/#W09}{{Dosono, B.}}, Ahmed, T., Kapadia, A., Semaan, B. (2019). Privacy implications of human intelligence powered assistive tools for visually impaired people. \textit{CHI 2019 Workshop on Bridging the Gap Between AI and HCI}. \\

& \footnotesize{[W1]} & Bayo, I., Budd, J., Caidi, N., Changfoot, N., Diaz Andrade, A., \href{https://doi.org/10.9776/14223}{{Dosono, B.}}, Gomez, R., Quan-Haase, A., Wolske, M. (2014). Information and marginality: Ethical issues. \textit{iConference 2014 Proceedings}. \\

\textcolor{black}{\footnotesize{\uppercase{Posters}}} & \footnotesize{[P3]} & Figueroa, J., Sullivan, J., Grimaldi, V., \href{https://www.ideals.illinois.edu/handle/2142/100251}{{Dosono, B.}} (2018). Finding a future beyond the field: Exploring ICT-mediated practices of student athletes. \textit{iConference 2018 Proceedings}. \\

& \footnotesize{[P2]} & \href{https://doi.org/10.9776/16575}{{Dosono, B.}}, Britton, L., Semaan, B. (2016). `Transition resilience' in veterans and refugees: Regaining normalcy after war. \textit{iConference 2016 Proceedings}. \\

& \footnotesize{[P1]} & \href{http://youtu.be/i5US90lHIac}{{Dosono, B.}}, Huynh, W., Liu, K., Lu, W. (2012). vTracker: Volunteer management web application. University of Washington Information School Capstone Fair. \textcolor{black}{Audience Choice Award.} \\

\textcolor{black}{\footnotesize{\uppercase{Doctoral Consortia}}} & \footnotesize{[DC5]} & \href{http://hicss.hawaii.edu/doctoral-consortium/}{{Dosono, B.}} (2019). Moderating identity work in online communities: The case of Asian American and Pacific Islanders on Reddit. \textit{Hawaii International Conference on System Sciences}. \\

& \footnotesize{[DC4]} & \href{https://aoir.org/}{{Dosono, B.}} (2018). Online identity work: The case of Asian Americans and Pacific Islanders on Reddit. \textit{Association of Internet Researchers}. \\

& \footnotesize{[DC3]} & \href{http://tapiaconference.org/schedule/wednesday-september-19-2018/100pm-500pm/doctoral-consortium/aapi-identity-work-on-reddit-toward-social-support-and-collective-action/}{{Dosono, B.}} (2018). AAPI identity work on Reddit. \textit{Richard Tapia Celebration of Diversity in Computing}. ACM. \\

& \footnotesize{[DC2]} & \href{https://ischools.org/the-iconference/program/doctoral-colloquium/2018-doctoral-colloquium/}{{Dosono, B.}} (2018). Identity work on Reddit: Social support and collective action of Asian Americans and Pacific Islanders. \textit{iConference 2018 Proceedings}. \\

& \footnotesize{[DC1]} & \href{https://dl.acm.org/authorize?N42808}{{Dosono, B.}} (2018). AAPI identity work on Reddit: Toward social support and collective action. \textit{Proceedings of the International Conference on Supporting Group Work}. ACM. \\

\textcolor{black}{\footnotesize{\uppercase{Book Chapters}}} 

& \footnotesize{[B2]} & \href{https://myersedpress.presswarehouse.com/browse/book/9781975500320/Fraternities-and-Sororities-in-the-Contemporary-Era}{{Dosono, B.}}, Badruddin, B., Lam, V. (2019). History of Asian American Fraternal Organizations. In Sasso, P. (2019). Foundations, Research, and Assessment of Fraternities and Sororities: Retrospective and Future Considerations. \textit{Myers Publishing}. (Forthcoming) \\

& \footnotesize{[B1]} & Gee, B., Seoh, H., \href{https://myersedpress.presswarehouse.com/browse/book/9781975500320/Fraternities-and-Sororities-in-the-Contemporary-Era}{{Dosono, B.}} (2019). The National Asian Pacific Islander Desi American Panhellenic Association. In Sasso, P. (2019). Supporting Fraternities and Sororities in the Contemporary Era: Advancements in Practice. \textit{Myers Publishing}. (Forthcoming) \\

\textcolor{black}{\footnotesize{\uppercase{Technical Reports}}}
& \footnotesize{[R4]} & Gee, B., \href{https://www.afa1976.org/page/AboutCFSR}{{Dosono, B.}}, Seoh, H. (2019). The National Asian Pacific Islander Desi American Panhellenic Association Resource Guide. Association of Fraternity/Sorority Advisors. (Forthcoming) \\

& \footnotesize{[R3]} & Biegel, B., \href{https://www.nasa.gov/digitalstrategy}{{Dosono, B.}}, Smith, T., Wang, M. (2019). Digital Transformation Media Review. NASA. (Forthcoming) \\

& \footnotesize{[R2]} & Ganghadaran, S., \href{https://www.newamerica.org/oti/policy-papers/virtually-unused/}{{Dosono, B.}}, Ngu, K. (2013). Virtually unused: Virtual private networks and public internet users. New America Foundation. \\

& \footnotesize{[R1]} & \href{http://youtu.be/Xob0hWqZQgU}{{Dosono, B.}} (2012). Digital inclusion: Developing an action plan for the City of Seattle. University of Washington Undergraduate Research Symposium. \\

\textcolor{black}{\footnotesize{\uppercase{Invited Talks}}} & \footnotesize{[T4]} & \href{https://news.syr.edu/blog/2019/03/22/celebrate-asian-american-and-pacific-islander-heritage-month-this-april/}{{Dosono, B.}} (2019). Syracuse University, Office of Multicultural Affairs. ``Decolonizing Asian American Institutions.'' \\

& \footnotesize{[T3]} & \href{https://cs.colgate.edu/cs/events/151/}{{Dosono, B.}} (2018). Colgate University, Department of Computer Science. ``Of shadow bans and sock puppets: Unraveling the deliberation and moderation of identity work on Reddit.'' \\

& \footnotesize{[T2]} & \href{http://www.sis.pitt.edu/i3/i3-cohorts/2017/schedule.html}{{Dosono, B.}} (2017). University of Pittsburgh, iSchool Inclusion Institute. ``Exploring Asian American and Pacific Islander identity work on Reddit.'' \\

& \footnotesize{[T1]} & Semaan, B., Britton, L., \href{http://bit.ly/CornellTalk}{{Dosono, B.}}, Bratt, S. (2017). Cornell University, Intercultural Communication Lab. ``Transition resilience with ICTs: The case of veteran re-integration.'' \\

\textcolor{black}{\footnotesize{\uppercase{Institutes}}} & \footnotesize{2018} & \href{https://www.oii.ox.ac.uk/blog/oii-sdp-cultivating-charismatic-cohorts/}{{Oxford Internet Institute Summer Doctoral Programme}} \\

& \footnotesize{2018} & \href{https://cra.org/events/urmgradcohort/}{{Computing Research Association Grad Cohort Workshop for Underrepresented Minorities + Persons with Disabilities}} \\

& \footnotesize{2015} & \href{http://graduateschool.syr.edu/programs/future-professoriate-program/}{{SU Future Professoriate Program Annual Conference}}
\\
\\
&&\par \Large \textcolor{black}{\uppercase{Service}}\\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Profession}}} 
& \footnotesize{2019} & \href{http://uist.acm.org/uist2019/}{{Reviewer}}, ACM Symposium on User Interface Software and Technology \\

& \footnotesize{2018} & \href{https://chi2018.acm.org}{{Session Chair \& Student Volunteer}}, ACM Conference on Human Factors in Computing Systems \\

& \footnotesize{2018} & \href{https://group.acm.org/conferences/group18/index.html}{{Student Volunteer}}, ACM International Conference on Supporting Group Work \\

& \footnotesize{2017} & \href{https://sigchi.org/}{{Student Volunteer}}, ACM SIGCHI Executive Committee \\

& \footnotesize{2017} & \href{https://chi2017.acm.org/}{{Reviewer \& Student Volunteer}}, ACM Conference on Human Factors in Computing Systems \\

& \footnotesize{2016} & \href{https://cscw.acm.org/}{{Reviewer}}, Computer-Supported Cooperative Work and Social Computing \\

& \footnotesize{2015} & \href{https://ischools.org/the-iconference/}{{Reviewer \& Student Volunteer Captain}}, iConference \\

& \footnotesize{2014} & \href{https://www.usenix.org/sites/default/files/soups14_proceedings.pdf}{{Reviewer}}, Symposium On Usable Privacy and Security \\

\textcolor{black}{\footnotesize{\uppercase{University}}} & \footnotesize{2019} & \href{http://dailyorange.com/2019/04/su-alum-deliver-lecture-industry-experience-cultural-identity-aapi-month/}{{Co-Chair}}, SU Office of Multicultural Affairs Asian American Pacific Islander Heritage Month \\

& \footnotesize{2015} & \href{http://gradresearch.syr.edu}{{Organizer}}, SU Graduate Forum on Research Methodologies \\

& \footnotesize{2014} & \href{http://gradorg.syr.edu/senate/committees/}{{Graduate Student Representative}}, SU Graduate Council \\

& \footnotesize{2014} & \href{http://gradorg.syr.edu/senate/committees/}{{Chair}}, SU Graduate Senate Academic Affairs Committee \\

& \footnotesize{2014} & \href{http://universitysenate.syr.edu/}{{Graduate Student Representative}}, SU Senate \\

& \footnotesize{2014} & \href{https://www.facebook.com/pg/sugrads/photos/?tab=album&album_id=874022975972914}{{Organizer}}, SU Graduate Research Symposium \\

& \footnotesize{2013} & \href{https://www.washington.edu/omad/2014/05/09/no-longer-invisible-bryan-dosono/}{{Student Representative}}, UW Office of Minority Affairs and Diversity Student Advisory Board \\

\textcolor{black}{\footnotesize{\uppercase{Department}}} & \footnotesize{2017} & 
 \href{https://ischool.syr.edu/facstaff/}{{Doctoral Representative}}, SU iSchool Hiring Committee \\

& \footnotesize{2014} & \href{https://ischool.syr.edu/facstaff/}{{Doctoral Representative}}, SU iSchool Personnel Committee \\

& \footnotesize{2013} & \href{https://ischool.syr.edu/facstaff/}{{Doctoral Representative}}, SU iSchool Faculty Committee \\

& \footnotesize{2013} & \href{http://dailyorange.com/2013/12/su-app-challenge-to-announce-winners-thursday/}{{Organizer}}, SU App Challenge \\

& \footnotesize{2012} & \href{https://ischool.uw.edu/current/career-services}{{Student Volunteer}}, UW Information School Research Fair \\

& \footnotesize{2012} & \href{https://web.archive.org/web/20130104065107/https://ischool.uw.edu/news/2012/11/annual-ischool-research-fair-showcases-faculty-and-student-work}{{Student Volunteer}}, UW Information School Career Fair \\

& \footnotesize{2011} & \href{https://ischool.uw.edu/about/leadership}{{Undergraduate Student Representative}}, UW Informatics Program Committee \\

\textcolor{black}{\footnotesize{\uppercase{Student Life}}} & \footnotesize{2017} & 
 \href{https://www.facebook.com/syracusefsa/}{{Founding Advisor}}, SU Filipino Student Association \\

& \footnotesize{2017} & \href{https://issuu.com/alinemagazine}{{Senior Editor}}, SU ALINE Magazine \\

& \footnotesize{2012} & \href{http://www.dailyuw.com/news/article_3c781595-0b4d-52be-9a6e-b2c956ae72eb.html}{{President}}, UW United Greek Council \\

& \footnotesize{2011} & \href{http://www.dailyuw.com/news/article_da48b049-d2a0-582c-9dfb-4589755ff1e5.html}{{Senate Speaker}}, Associated Students of the University of Washington \\

& \footnotesize{2010} & \href{https://www.washington.edu/giving/get-involved/for-students/real-dawgs-give-back/}{{Founder}}, UW Student Philanthropy Education Program \\

& \footnotesize{2009} & \href{https://honors.uw.edu/community/grads/12_13/}{{Mentor}}, UW Honors Program \\

\textcolor{black}{\footnotesize{\uppercase{Speaking}}} & \footnotesize{2018} & \href{https://www.facebook.com/events/170505843576915/}{{Panelist}}, Syracuse Professional Fraternity Council \\

& \footnotesize{2017} & \href{http://www.suwise.syr.edu/}{{Workshop Presenter}}, Syracuse Women in Science and Engineering Program \\

& \footnotesize{2016} & \href{https://www.ecaasu.org/}{{Workshop Presenter}}, East Coast Asian American Student Union Conference \\

& \footnotesize{2015} & \href{http://www.mortarboard.org/conference/}{{Panelist}}, Mortar Board National Conference \\

& \footnotesize{2013} & \href{https://youtu.be/uz1tukrR-7E}{{Commencement Speaker}}, UW Filipino American Student Association Graduation \\

& \footnotesize{2012} & \href{https://youtu.be/WMPhe6H7yiM}{{Keynote Speaker}}, UW Spring Leadership and Service Symposium \\

& \footnotesize{2012} & \href{https://ischool.uw.edu/news/2016/12/bryan-dosono-informatics-student-speaks-boeing-scholarship-breakfast}{{Keynote Speaker}}, UW Boeing Donor Scholarship Breakfast \\

& \footnotesize{2008} & \href{https://youtu.be/5gt7nFRgkac}{{Commencement Speaker}}, Wapato High School Valedictorian Address \\

\textcolor{black}{\footnotesize{\uppercase{Community}}} & \footnotesize{2017} & \href{http://www.napahq.org/}{{Director of Technology}}, National Asian Pacific Islander Desi American Panhellenic Association \\

& \footnotesize{2016} & \href{https://www.facebook.com/events/215634702135825/}{{Organizer}}, National Asian American Pacific Islander Mental Health Association Mental Health Summit \\

& \footnotesize{2013} & \href{https://www.capal.org/programs/wlp/}{{Washington Leadership Program}}, Conference on Asian Pacific American Leadership \\

& \footnotesize{2012} & \href{http://www.dailyuw.com/news/article_de3524ce-3d5e-5dd2-8de7-5deebee463d9.html}{{Volunteer Coordinator}}, National Marrow Donor Program \\

& \footnotesize{2009} & \href{http://www.washington.edu/news/2010/04/22/student-service-and-leadership-to-be-celebrated-april-28/}{{Hardware Refurbisher}}, InterConnection \\

\textcolor{black}{\footnotesize{\uppercase{Public Appointments}}} & \footnotesize{2015} & \href{https://sites.ed.gov/aapi/e3-ambassadors/}{{Ambassador}}, White House Initiative on Asian Americans and Pacific Islanders \\

& \footnotesize{2011} & \href{https://web.archive.org/web/20150911093548/https://ischool.uw.edu/alumni/impact-stories/informatics-grad-and-husky-promise-student-aims-deliver-it-resources}{{Commissioner}}, City of Seattle Community Technology Advisory Board \\

\textcolor{black}{\footnotesize{\uppercase{Memberships}}} & \footnotesize{2018} & \href{https://www.nyas.org/}{{New York Academy of Sciences}} (NYAS), Active \\

 & \footnotesize{2017} & \href{https://www.sigchi.org/}{{Special Interest Group on Computer-Human Interaction}} (SIGCHI), Active \\

& \footnotesize{2013} & \href{https://www.acm.org/}{{Association for Computing Machinery}} (ACM), Active \\

& \footnotesize{2013} & \href{https://www.ieee.org/}{{Institute of Electrical and Electronics Engineers}} (IEEE), Active \\

& \footnotesize{2008} & \href{https://www.asist.org/}{{Association for Information Science and Technology}} (ASIS\&T)
\\
\\
&&\par \Large \textcolor{black}{\uppercase{Awards}}\\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Travel Grants}}} & \footnotesize{2018} & \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1823052}{{National Science Foundation: ACM Richard Tapia Celebration of Diversity in Computing Conference Travel Grant}} (\$1,348) \\

& \footnotesize{2018} & \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1713738}{{National Science Foundation: iConference 2018 Doctoral Colloquium Travel Grant}} (\$1,845) \\

& \footnotesize{2018} & \href{https://cra.org/events/urmgradcohort/}{{CRA Grad Cohort Workshop Travel Grant}} (\$900) \\

& \footnotesize{2018} & \href{https://dl.acm.org/citation.cfm?id=3148330}{{ACM GROUP Doctoral Consortium Travel Grant}} (\$1,000) \\

& \footnotesize{2017} & \href{http://gradorg.syr.edu/}{{SU Graduate Student Organization Travel Grant}} (\$900) \\

& \footnotesize{2017} & \href{https://sigchi.org/2017/03/sigchi-sponsors-students-to-attend-turing-award-celebration/}{{ACM SIGCHI 50th Celebration of the Turing Award Student Scholarship}} (\$900) \\

& \footnotesize{2016} & \href{https://sigchi.org/conferences/student-travel-grants/sigchi-student-travel-grant/}{{ACM SIGCHI Student Travel Grant}} (\$1,500) \\

& \footnotesize{2016} & \href{https://ischool.syr.edu/research/grants-and-awards/}{{SU iSchool Doctoral Travel Grant}} (\$800) \\

& \footnotesize{2015} & \href{https://cups.cs.cmu.edu/soups/2015/cfp.php}{{Symposium on Usable Privacy and Security Travel Grant}} (\$500) \\

& \footnotesize{2015} & \href{https://ischool.syr.edu/research/grants-and-awards/}{{SU iSchool Doctoral Travel Grant}} (\$700) \\

\textcolor{black}{\footnotesize{\uppercase{Fellowships}}} & \footnotesize{2018} & \href{https://forum2018.diglib.org/fellowship-opportunities/fellows/}{{Digital Library Federation New Professional Fellowship}} (\$1,000) \\

& \footnotesize{2016} & \href{http://www.sis.pitt.edu/i3/phd-fellows/fellow-profiles.html}{{iSchool Inclusion Institute Teaching Fellowship}} (\$1,000) \\

& \footnotesize{2016} & \href{https://www.bankofamerica.com/philanthropic/foundation.go?fnId=31}{{Lloyd G. Balfour Foundation Fellowship}} (\$1,000) \\

& \footnotesize{2015} & \href{https://news.syr.edu/2015/07/ischool-student-awarded-5000-mortar-board-fellowship-22021/}{{Mortar Board Graduate Fellowship}} (\$5,000) \\

& \footnotesize{2015} & \href{https://news.syr.edu/2012/04/ischool-advisersu-trustee-creates-new-summer-ph-d-fellowships/}{{Dean's Fellowship}} (\$7,000) \\

& \footnotesize{2013} & \href{https://www.google.com/policyfellowship/2013fellows.html}{{Google Policy Fellowship}} (\$7,500) \\

& \footnotesize{2013} & \href{https://www.syracuse.edu/admissions/cost-and-aid/types-of-aid/graduate-student-aid/fellowships/}{{Ronald E. McNair Graduate Fellowship}} (\$23,135) \\

& \footnotesize{2009} & \href{https://www.washington.edu/carlson/ellis-civic-fellowship/}{{Robert Lee Ellis Civic Fellowship}} (\$12,000) \\

\textcolor{black}{\footnotesize{\uppercase{Scholarships}}} & \footnotesize{2018} & \href{https://www.afa1976.org/foundation}{{Thomas B. Jelke Graduate Scholarship}} (\$300) \\

& \footnotesize{2014} & \href{https://youtu.be/kFmO44rs3-c}{{SU Katzer Research Fund}} (\$11,000) \\

& \footnotesize{2013} & \href{https://expo.uw.edu/public/offering/271}{{Bill and Melinda Gates Foundation Research Scholarship}} (\$4,000) \\

& \footnotesize{2012} & \href{https://depts.washington.edu/eip/}{{Early Identification Program Presidential Scholarship}} (\$3,500) \\

& \footnotesize{2012} & \href{https://www.nsf.gov/crssprgm/reu/}{{National Science Foundation Research Experience for Undergraduates Grant}} (\$6,399) \\

& \footnotesize{2012} & \href{https://www.washington.edu/uaa/2013/06/28/oh-the-places-theyll-go-new-grads-and-their-plans/bryan-dosono/}{{University of Washington Homecoming King Royalty Scholarship }}(\$1,000) \\

& \footnotesize{2011} & \href{https://ischool.uw.edu/news/2016/12/bryan-dosono-informatics-student-speaks-boeing-scholarship-breakfast}{{Boeing Diversity Scholarship}} (\$3,000) \\

& \footnotesize{2011} & \href{https://www.washington.edu/omad/2011/05/17/assunta-ng-student-scholars-honored-at-41st-annual-eop-celebration/}{{Ruth and William Gerberding Scholarship}} (\$2,000) \\

& \footnotesize{2011} & \href{http://lambdaphiepsilon.com/resources/\#academicachievement}{{Lambda Phi Epsilon International Brother of the Year Scholarship}} (\$1,500) \\

& \footnotesize{2010} & \href{https://depts.washington.edu/uwhonors/news/brief/?id=61}{{Benjamin A. Gilman International Scholarship}} (\$3,000) \\

& \footnotesize{2010} & \href{https://www2.ed.gov/programs/smart/index.html}{{National Science and Math Access to Retain Talent Grant}} (\$1,333) \\

& \footnotesize{2008} & \href{https://www.wsac.wa.gov/}{{Washington Scholar Full Tuition Scholarship}} (\$30,000) \\

& \footnotesize{2008} & \href{https://www.elks.org/enf/scholars/}{{Elks National Foundation Scholarship}} (\$7,000) \\

& \footnotesize{2008} & \href{https://www.dellscholars.org/}{{Dell Scholars Foundation Scholarship}} (\$20,000) \\

\textcolor{black}{\footnotesize{\uppercase{Honors}}} 
& \footnotesize{2019} & 
\href{https://news.syr.edu/blog/2019/04/29/44-stars-of-excellence-awards-honor-members-of-campus-community/}{{SU Office of Multicultural Affairs' Irma Almirall-Padamsee La Fuerza Community Enhancement Award}} \\

& \footnotesize{2019} &\href{https://news.syr.edu/blog/2019/04/29/44-stars-of-excellence-awards-honor-members-of-campus-community/}{{SU Award for Excellence by an Organizational Advisor}} \\

& \footnotesize{2013} &
\href{https://twitter.com/bdosono/status/1082439167512961024}{{Association for Information Systems, Hawaii International Conference on System Sciences Doctoral Fellow}} \\

& \footnotesize{2013} & \href{https://ischool.uw.edu/news/2016/12/2013-ischool-convocation-celebrates-achievement-and-community}{{UW Faculty Award for Student Excellence in Informatics}} \\

& \footnotesize{2013} & \href{https://www.washington.edu/omad/celebration/recognition-scholarship-recipients/2013-celebration-scholarship-recipients/}{{UW President's Achievement Award}} \\

& \footnotesize{2013} & \href{https://depts.washington.edu/thehub/hub-events/hub-awards/}{{UW Hall of Fame Inductee for Outstanding Contributions to Student Activities}} \\

& \footnotesize{2013} & \href{https://www.facebook.com/EthnicCulturalCenter/photos/a.10151638127531422.1073741830.124987626421/10151638128881422/}{{UW Ethnic Cultural Center Director's Outstanding Leadership Award}} \\

& \footnotesize{2013} & \href{https://www.facebook.com/UWiSchool/posts/10151645734368695}{{UW Commencement Gonfaloniere}} \\

& \footnotesize{2013} & \href{https://www.yakimaherald.com/news/education/school-news-sept/article_af5885a3-bcbc-5925-bb87-a84844c6d36a.html}{{UW Dean's List}} \\

& \footnotesize{2012} & \href{http://orderofomega.org/}{{Order of Omega}} \\

& \footnotesize{2011} & \href{https://www.pbk.org/}{{Phi Beta Kappa}} \\

\textcolor{black}{\footnotesize{\uppercase{Press}}} 

& \footnotesize{2019} & \href{https://ischool.syr.edu/articles/news/view/three-doctoral-grads-taking-diverse-career-pathways-2019/}{\textit{{Syracuse University iSchool News}}}, ``Three doctoral grads taking diverse career pathways'' \\

& \footnotesize{2019} & \href{http://dailyorange.com/2019/04/aapi-heritage-month-exhibit-remembers-su-campus-hate-crime-raises-awareness/}{\textit{{The Daily Orange}}}, ``AAPI Heritage Month exhibit remembers SU campus hate crime, raises awareness'' \\

& \footnotesize{2019} & \href{https://ischool.syr.edu/articles/news/view/faculty-students-presenting-at-iconference-2019/}{\textit{{Syracuse University iSchool News}}}, ``Faculty, students presenting at iConference 2019'' \\

& \footnotesize{2018} & \href{https://issuu.com/alist_magazine/docs/alist_summer_2018_final}{\textit{{ALIST Magazine}}}, ``The intersection of technology, innovation and human values with Bryan Dosono'' \\

& \footnotesize{2018} & \href{http://dailyorange.com/2018/04/asian-american-pacific-islander-students-celebrate-place-syracuse-university/}{\textit{{The Daily Orange}}}, ``Asian American and Pacific Islander students celebrate their place at Syracuse University'' \\

& \footnotesize{2018} & \href{https://ischool.syr.edu/articles/news/view/faculty-students-presenting-iconference-2018/}{\textit{{Syracuse University iSchool News}}}, ``Faculty, students presenting at iConference 2018'' \\

& \footnotesize{2017} & \href{https://ischool.syr.edu/articles/news/view/dosono-to-attend-acm-turing-award-celebration/}{\textit{{Syracuse University iSchool News}}}, ``Dosono to attend ACM's Turing Award Celebration'' \\

& \footnotesize{2017} & \href{https://ischool.syr.edu/articles/news/view/faculty-staff-phd-students-presenting-iconference-2017/}{\textit{{Syracuse University iSchool News}}}, ``Faculty, staff, doctoral students presenting at iConference 2017'' \\

& \footnotesize{2016} & \href{https://issuu.com/kiefercreative/docs/suischool-connections-sp2016}{\textit{{Connections Magazine}}}, ``iSchool researchers use technology to understand veteran reacclimation'' \\

& \footnotesize{2016} & \href{https://ischool.syr.edu/articles/news/view/faculty-phd-students-presenting-at-iconference-2016/}{\textit{{Syracuse University iSchool News}}}, ``Faculty, doctoral students presenting at iConference'' \\

& \footnotesize{2015} & \href{https://ischool.syr.edu/articles/news/view/research-in-privacy-security-profiled-at-soups-conference/}{\textit{{Syracuse University iSchool News}},} ``Research in privacy, security being profiled at SOUPS Conference'' \\

& \footnotesize{2014} & \href{http://dailyorange.com/2014/11/ischool-research-aims-to-aid-military-veterans-refugees/}{\textit{{The Daily Orange}},} ``iSchool research aims to aid military veterans, refugees'' \\

& \footnotesize{2014} & \href{https://ischool.syr.edu/articles/news/view/faculty-doctoral-students-presenting-at-iconference/}{\textit{{Syracuse University iSchool News}}}, ``Faculty, doctoral students presenting at iConference'' \\

& \footnotesize{2014} & \href{https://issuu.com/uwalumni/docs/viewpoint_2014fall}{\textit{{Viewpoint}}, }``The husky experience'' \\

& \footnotesize{2013} & \href{http://dailyorange.com/2013/10/su-app-challenge-offers-1000-grand-prize/}{\textit{{The Daily Orange}}}, ``SU app challenge offers \$1,000 grand prize'' \\

& \footnotesize{2013} & \href{http://www.nwasianweekly.com/2013/07/uw-2013-eop-celebration-honors-3-apa-students/}{\textit{{Northwest Asian Weekly}}}, ``EOP celebration honors 3 APA students'' \\

& \footnotesize{2013} & \href{https://www.yakimaherald.com/news/local/wapato-resident-receives-uw-honor/article_c7041e94-ace9-5168-a364-d0b9206a6a41.html}{\textit{{Yakima Herald Independent}}}, ``Wapato resident receives UW honor'' \\

& \footnotesize{2013} & \href{http://www.dailyuw.com/news/article_e5e0683f-d959-5ce1-b1f2-4d23e797b379.html}{\textit{{UW Daily}}}, ``ECC honors community members for activism efforts" \\
\end{longtable}}
\end{document}}