\documentclass[12pt]{article}
\usepackage{array}
\usepackage{ragged2e}
\usepackage[svgnames,table]{xcolor}
\color{gray}
\usepackage{longtable}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{hhline}
\usepackage{multicol}
\usepackage{lastpage}
\usepackage{multirow}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage[paperheight=11.0in,paperwidth=8.5in,top=1in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage[none]{hyphenat}
\usepackage{fontspec}
\setmainfont[AutoFakeSlant=0.3]{Rasa}

\hypersetup{colorlinks,allcolors=[HTML]{0B5394},pdfinfo={Title={Curriculum Vitae of Bryan Dosono},Author={Bryan Dosono},Creator={Bryan Dosono},Subject={Curriculum Vitae},Keywords={Curriculum Vitae},CreationDate={D:20181014232724}}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\pagestyle{fancy}
\fancyhf{}
\cfoot{
\vspace*{0in}
\textcolor{grey}{
\begin{tabular}{Rp{1.0in}p{0.2in}|p{4.8in}}
& {\footnotesize{\thepage/5}} & { \footnotesize{Dosono, CV}} \\
\end{tabular}}}

\renewcommand{\headrulewidth}{0pt}
\setlength{\topsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\renewcommand{\arraystretch}{1}
%\renewcommand{\baselinestretch}{1.1}
%\setlength\tabcolsep{0pt}

\definecolor{grey}{HTML}{3E3D3C}
\begin{document} 
{\RaggedRight {\color{grey}
\setlength \extrarowheight{2pt}
\begin{longtable}{Rp{1.0in}p{0.25in}p{4.75in}}

&& \Huge \textcolor{black}{\uppercase{Bryan Dosono}} \par \normalsize \href{mailto:info@bdosono.com}{{info@bdosono.com}} $\vcenter{\hbox{\tiny$\bullet$}}$ \href{http://www.bdosono.com/}{{www.bdosono.com}} \par Curriculum Vitae, February 2019  \bigskip \\

&& \par \Large \textcolor{black}{\uppercase{Education}} \\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Doctor of Philosophy}}} & \footnotesize{2019} & \href{http://ischool.syr.edu/bdosono}{{Ph.D. in Information Science and Technology}} \textit{(Expected 2019)} \par Syracuse University (SU), School of Information Studies, Syracuse, NY \par Concentration: Data Science \\

\textcolor{black}{\footnotesize{\uppercase{Bachelor of Science}}} & \footnotesize{2013} & \href{https://web.archive.org/web/20140402144404/http://ischool.uw.edu/research/student-research/dosono}{{B.S. in Informatics: Human-Computer Interaction}} \par University of Washington (UW), Information School, Seattle, WA \par College Honors, Phi Beta Kappa, Magna Cum Laude, Minor: Music \\  

\\

&&\par \Large \textcolor{black}{\uppercase{Employment}}\\ \hhline{~~-} 

\textcolor{black}{\footnotesize{\uppercase{Academic}}} & \footnotesize{2019} & \href{http://bits.ischool.syr.edu/}{{Doctoral Researcher}}, Syracuse University \\ && \textcolor{black}{Research}: Behavior, Information, Technology and Society Laboratory (Research Assistant); Social Computing Systems Laboratory (Research Assistant) \\ && \textcolor{black}{Teaching}: Human-Computer Interaction (Guest Lecturer); Introduction to Asian American Studies (Guest Lecturer); Theories of Digital Technology (Teaching Assistant); Information Reporting and Presentation (Teaching Assistant); Social Web Technologies (Teaching Assistant) \\

& \footnotesize{2016} & \href{http://www.sis.pitt.edu/i3/phd-fellows/fellow-profiles.html}{{Teaching Fellow}}, University of Pittsburgh \\ &&\textcolor{black}{Research}: iSchool Inclusion Institute (Advisor) \\ &&\textcolor{black}{Teaching}: Python Programming (Instructor) \\

\textcolor{black}{\footnotesize{\uppercase{Industry}}} & \footnotesize{2018} & \href{https://www.airbnb.com/}{{Experience Research Ph.D. Intern}}, Airbnb \\

& \footnotesize{2018} & \href{https://vsfs.state.gov/about}{{Virtual Student Federal Service Research Intern}}, National Aeronautics and Space Administration \\

& \footnotesize{2013} & \href{https://www.google.com/policyfellowship/2013fellows.html}{{Google Policy Fellow}}, New America Foundation Open Technology Institute \\

\\

&&\par \Large \textcolor{black}{\uppercase{Research}} \\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Dissertation}}} & \footnotesize{[D1]} &  \href{https://ischool.syr.edu/events/view/proposal-defense-bryan-dosono/}{{Dosono, B.}} (2019). Identity work of Asian Americans and Pacific Islanders on Reddit: Traversals of deliberation, moderation, and decolonization. (Forthcoming). \\

\textcolor{black}{\footnotesize{\uppercase{Peer-reviewed Journal Publications}}} & \footnotesize{[J3]} & \href{https://doi.org/10.1109/MIC.2018.112101619}{{Dosono, B.}}, Hayes, J., Wang, Y. (2018). Toward accessible authentication: Learning from people with visual impairments. \textit{IEEE Internet Computing}, 22(2). \\

& \footnotesize{[J2]} & \href{https://dl.acm.org/authorize?N42807}{{Dosono, B.}}, Rashidi, Y., Akter, T., Semaan, B., Kapadia, A. (2017). Challenges in transitioning from civil to military culture: Hyper-selective disclosure through ICTs. \textit{Proceedings of the ACM on Human-Computer Interaction}, 1. ACM. \\

& \footnotesize{[J1]} & Gomez, R., Pather, S., \href{https://doi.org/10.1002/j.1681-4835.2012.tb00366.x}{{Dosono, B.}} (2012). Public access computing in South Africa: Old lessons and new challenges. \textit{The Electronic Journal of Information Systems in Developing Countries}, 52(1). \\

\textcolor{black}{\footnotesize{\uppercase{Peer-reviewed Conference Proceedings}}} & \footnotesize{[C14]} & \href{https://chi2019.acm.org/}{{Dosono, B.}}, Semaan, B. (2019). Moderation practices as emotional labor in sustaining online communities: The case of AAPI identity work on Reddit. \textit{Proceedings of the 37th Annual ACM Conference on Human Factors in Computing Systems}. ACM. Forthcoming. \\

& \footnotesize{[C13]} & Grimaldi, V., Figueroa, J., Sullivan, J., \href{https://www.conftool.com/iConference2019/sessions.php}{{Dosono, B.}} (2019). From gridiron gang to game plan: Impact of ICTs on student athlete information seeking practices, routines, and long-term goals. iConference 2019. \textit{Lecture Notes in Computer Science}. Springer, Cham. Forthcoming. \\

& \footnotesize{[C12]} & \href{https://dl.acm.org/authorize?N658208}{{Dosono, B.}}, Semaan, B. (2018). Identity work as deliberation: AAPI political discourse in the 2016 US Presidential Election. \textit{Proceedings of the 36th Annual ACM Conference on Human Factors in Computing Systems}. ACM. \\

& \footnotesize{[C11]} & Booth, K., \href{https://doi.org/10.1007/978-3-319-78105-1_75}{ {Dosono, B.}}, Redmiles, E., Morales, M., Depew, M., Herman, E., Trahan, K., Tananis, C., Farzan, R. (2018). Diversifying the next generation of information scientists: Six years of implementation and outcomes for a year-long REU program. In Transforming Digital Worlds. iConference 2018. \textit{Lecture Notes in Computer Science} (pp. 655-664). Springer, Cham. \\

& \footnotesize{[C10]} & \href{http://dl.acm.org/authorize?N41342}{{Dosono, B.}}, Semaan, B., Hemsley, J. (2017). Exploring AAPI identity online: Political ideology as a factor affecting identity work on Reddit. \textit{Proceedings of the 2017 CHI Conference Extended Abstracts on Human Factors in Computing Systems }(pp. 2528-2535). ACM. \\

& \footnotesize{[C9]} & Bratt, S., Semaan, B., Britton, L., \href{http://idl.iscram.org/files/sarahbratt/2017/1463\_SarahBratt\_etal2017.pdf}{{Dosono, B.}}, Franco, Z. (2017). Translation in personal crises: Opportunities for wearables design. \textit{Proceedings of the Conference on Information Systems for Crisis Response and Management.} \\

& \footnotesize{[C8]} & Hayes, J., \href{http://hdl.handle.net/2142/96755}{{Dosono, B.}}, Wang, Y. (2017). ``They should be convenient and strong'': Password perceptions and practices of visually impaired users. \textit{iConference 2017 Proceedings.} \\

& \footnotesize{[C7]} & Semaan, B., \href{http://dl.acm.org/authorize?N41343}{{Dosono, B.}}, Britton, L. (2017). Impression management in high context societies: ‘Saving face’ with ICT. \textit{Proceedings of the 2017 ACM Conference on Computer Supported Cooperative Work and Social Computing} (pp. 712-725). ACM. \\

& \footnotesize{[C6]} & Semaan, B., Britton, L., \href{http://dl.acm.org/authorize?N41344}{{Dosono, B.}} (2017). Military masculinity and the travails of transitioning: Disclosure in social media. \textit{Proceedings of the 2017 ACM Conference on Computer Supported Cooperative Work and Social Computing} (pp. 387-403). ACM. \\

& \footnotesize{[C5]} & Semaan, B., Britton, L., \href{http://dl.acm.org/authorize?N41455}{{Dosono, B.}} (2016). Transition resilience with ICTs: ‘Identity awareness’ in veteran reintegration. \textit{Proceedings of the 34th Annual ACM Conference on Human Factors in Computing Systems} (pp. 2882-2894). ACM. \\

& \footnotesize{[C4]} & \href{http://hdl.handle.net/2142/89438}{{Dosono, B.}} (2016). Patron privacy: A luxury concern for marginalized Internet users.\textit{ iConference 2016 Proceedings}. \\

& \footnotesize{[C3]} & \href{https://www.usenix.org/conference/soups2015/proceedings/presentation/dosono}{{Dosono, B.}}, Hayes, J., Wang, Y. (2015). ``I’m stuck!'': A contextual inquiry of people with visual impairment in authentication. \textit{Symposium On Usable Privacy and Security} (pp. 151-168). USENIX Association. \\

& \footnotesize{[C2]} & \href{http://www.ideals.illinois.edu/handle/2142/47321}{{Dosono, B.}} (2014). Digital inclusion for migrant millennials: Improving the ICT landscape of Yakima Valley Schools. \textit{iConference 2014 Proceedings}. \\

& \footnotesize{[C1]} & Ko, A., \href{http://dl.acm.org/authorize?N41457}{{Dosono, B.}}, Duriseti, N. (2014). Thirty years of software problems in the news. \textit{Proceedings of the 7th International Workshop on Cooperative and Human Aspects of Software Engineering} (pp.32-39). ACM. \\

\textcolor{black}{\footnotesize{\uppercase{Workshops Organized}}} & \footnotesize{[W1]} & Bayo, I., Budd, J., Caidi, N., Changfoot, N., Diaz Andrade, A., \href{http://www.ideals.illinois.edu/handle/2142/47393}{{Dosono, B.}}, Gomez, R., Quan-Haase, A., Wolske, M. (2014). Information and marginality: Ethical issues. \textit{iConference 2014 Proceedings}. \\

\textcolor{black}{\footnotesize{\uppercase{Posters}}} & \footnotesize{[P3]} & Figueroa, J., Sullivan, J., Grimaldi, V., \href{https://www.ideals.illinois.edu/handle/2142/100251}{{Dosono, B.}} (2018). Finding a future beyond the field: Exploring ICT-mediated practices of student athletes. \textit{iConference 2018 Proceedings}. \\

& \footnotesize{[P2]} & \href{http://hdl.handle.net/2142/89348}{{Dosono, B.}}, Britton, L., Semaan, B. (2016). ‘Transition resilience’ in veterans and refugees: Regaining normalcy after war. \textit{iConference 2016 Proceedings}. \\

& \footnotesize{[P1]} & \href{http://youtu.be/i5US90lHIac}{{Dosono, B.}}, Huynh, W., Liu, K., Lu, W. (2012). vTracker: Volunteer management web application. University of Washington Information School Capstone Fair. \textcolor{black}{Audience Choice Award.} \\

\textcolor{black}{\footnotesize{\uppercase{Book Chapters}}} & \footnotesize{[B1]} & \href{http://myersedpress.com/BookDetail.aspx?productID=536594}{{Dosono, B.}}, Badruddin, B., Lam, V. (2019). History of Asian American Fraternal Organizations. In Sasso, P. (2019). Fraternities and Sororities in the Contemporary Era: A Pendulum of Tolerance. \textit{Myers Publishing}. (Forthcoming) \\

\textcolor{black}{\footnotesize{\uppercase{Technical Reports}}} & \footnotesize{[R2]} & Ganghadaran, S., \href{http://newamerica.net/publications/policy/virtually_unused}{{Dosono, B.}}, Ngu, K. (2013). Virtually unused: Virtual private networks and public internet users. New America Foundation. \\

& \footnotesize{[R1]} & \href{http://youtu.be/Xob0hWqZQgU}{{Dosono, B.}} (2012). Digital inclusion: Developing an action plan for the City of Seattle. University of Washington Undergraduate Research Symposium, Seattle, WA. \\

\textcolor{black}{\footnotesize{\uppercase{Invited Talks}}} & \footnotesize{[T3]} & \href{https://cs.colgate.edu/cs/events/151/}{{Dosono, B.}} (2018). Colgate University, Department of Computer Science. ``Of shadow bans and sock puppets: Unraveling the deliberation and moderation of identity work on Reddit.'' \\

& \footnotesize{[T2]} & \href{http://www.sis.pitt.edu/i3/i3-cohorts/2017/schedule.html}{{Dosono, B.}} (2017). University of Pittsburgh, iSchool Inclusion Institute. ``Exploring Asian American and Pacific Islander identity work on Reddit.'' \\

& \footnotesize{[T1]} & Semaan, B., Britton, L., \href{http://bit.ly/CornellTalk}{{Dosono, B.}}, Bratt, S. (2017). Cornell University, Intercultural Communication Lab. ``Transition resilience with ICTs: The case of veteran re-integration.'' \\

\textcolor{black}{\footnotesize{\uppercase{Institutes}}} & \footnotesize{2018} & \href{https://www.oii.ox.ac.uk/blog/oii-sdp-cultivating-charismatic-cohorts/}{{Oxford Internet Institute Summer Doctoral Programme}} \\

& \footnotesize{2018} & \href{https://cra.org/events/urmgradcohort/}{{Computing Research Association Grad Cohort Workshop for Underrepresented Minorities + Persons with Disabilities}} \\

& \footnotesize{2015} & \href{http://graduateschool.syr.edu/programs/future-professoriate-program/}{{Syracuse University Future Professoriate Program Annual Conference}} \bigskip \\

&&\par \Large \textcolor{black}{\uppercase{Service}}\\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Profession}}} & \footnotesize{2018} & \href{https://chi2018.acm.org}{{Session Chair $\&$  Student Volunteer}}, ACM Conference on Human Factors in Computing Systems \\

& \footnotesize{2018} & \href{http://group.acm.org/conferences/group18/index.html}{{Student Volunteer}}, ACM International Conference on Supporting Group Work \\

& \footnotesize{2017} & \href{https://sigchi.org/}{{Student Volunteer}}, ACM SIGCHI Executive Committee \\

& \footnotesize{2017} & \href{https://chi2017.acm.org/}{{Reviewer}} \href{http://ischools.org/the-iconference/}{{$\&$  Student Volunteer}}, ACM Conference on Human Factors in Computing Systems \\

& \footnotesize{2016} & \href{https://cscw.acm.org/}{{Reviewer}}, Computer-Supported Cooperative Work and Social Computing \\

& \footnotesize{2015} & \href{http://ischools.org/the-iconference/}{{Reviewer $\&$  Student Volunteer Captain}}, iConference \\

& \footnotesize{2014} & \href{https://www.usenix.org/sites/default/files/soups14_proceedings.pdf}{{Reviewer}}, Symposium On Usable Privacy and Security \\

\textcolor{black}{\footnotesize{\uppercase{University}}} & \footnotesize{2019} & \href{http://dailyorange.com/2018/04/asian-american-pacific-islander-students-celebrate-place-syracuse-university/}{{Co-Chair}}, SU Office of Multicultural Affairs Asian American Pacific Islander Heritage Month \\

& \footnotesize{2015} & \href{http://gradresearch.syr.edu}{{Organizer}}, SU Graduate Forum on Research Methodologies \\

& \footnotesize{2014} & \href{http://gradorg.syr.edu/senate/committees/}{{Graduate Student Representative}}, SU Graduate Council \\

& \footnotesize{2014} & \href{http://gradorg.syr.edu/senate/committees/}{{Chair}}, SU Graduate Senate Academic Affairs Committee \\

& \footnotesize{2014} & \href{http://universitysenate.syr.edu/}{{Graduate Student Representative}}, SU Senate \\

& \footnotesize{2014} & \href{https://www.facebook.com/sugrads/photos/tab=album\&album\_id=874022975972914}{{Organizer}}, SU Graduate Research Symposium \\

& \footnotesize{2013} & \href{http://www.washington.edu/omad/2014/05/09/no-longer-invisible-bryan-dosono/}{{Student Representative}}, UW Office of Minority Affairs and Diversity Student Advisory Board \\

\textcolor{black}{\footnotesize{\uppercase{Community}}} & \footnotesize{2017} & \href{http://napahq.org}{{Director of Technology}}, National Asian Pacific Islander Desi American Panhellenic Association \\

& \footnotesize{2016} & \href{https://www.facebook.com/events/215634702135825/}{{Organizer}}, National Asian American Pacific Islander Mental Health Association Mental Health Summit \\

& \footnotesize{2013} & \href{http://www.capal.org/programs/wlp/}{{Washington Leadership Program}}, Conference on Asian Pacific American Leadership \\

& \footnotesize{2012} & \href{http://www.dailyuw.com/news/article_de3524ce-3d5e-5dd2-8de7-5deebee463d9.html}{{Volunteer Coordinator}}, National Marrow Donor Program \\

& \footnotesize{2009} & \href{http://www.washington.edu/news/2010/04/22/student-service-and-leadership-to-be-celebrated-april-28/}{{Hardware Refurbisher}}, InterConnection \\

\textcolor{black}{\footnotesize{\uppercase{Public Appointments}}} & \footnotesize{2015} & \href{http://sites.ed.gov/aapi/e3-ambassadors/}{{Ambassador}}, White House Initiative on Asian Americans and Pacific Islanders \\

& \footnotesize{2011} & \href{https://web.archive.org/web/20150911093548/https://ischool.uw.edu/alumni/impact-stories/informatics-grad-and-husky-promise-student-aims-deliver-it-resources}{{Commissioner}}, City of Seattle Community Technology Advisory Board \\

\textcolor{black}{\footnotesize{\uppercase{Memberships}}} & \footnotesize{2018} & \href{https://www.nyas.org/}{{New York Academy of Sciences}} (NYAS), Active \\

 & \footnotesize{2017} & \href{http://www.sigchi.org/}{{Special Interest Group on Computer-Human Interaction}} (SIGCHI), Active \\

& \footnotesize{2013} & \href{https://www.acm.org/}{{Association for Computing Machinery}} (ACM), Active \\

& \footnotesize{2013} & \href{https://www.ieee.org/}{{Institute of Electrical and Electronics Engineers}} (IEEE), Active \\

& \footnotesize{2008} & \href{https://www.asist.org/}{{Association for Information Science and Technology}} (ASIS\&T)

\\

&&\par \Large \textcolor{black}{\uppercase{Awards}}\\ \hhline{~~-}

\textcolor{black}{\footnotesize{\uppercase{Travel Grants}}} & \footnotesize{2018} & \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1823052}{{National Science Foundation: ACM Richard Tapia Celebration of Diversity in Computing Conference Travel Grant}} (\$1,348) \\

& \footnotesize{2018} & \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1713738}{{National Science Foundation: iConference 2018 Doctoral Colloquium Travel Grant}} (\$1,845) \\

& \footnotesize{2018} & \href{https://cra.org/events/urmgradcohort/}{{CRA Grad Cohort Workshop Travel Grant} }(\$900) \\

& \footnotesize{2018} & \href{https://dl.acm.org/citation.cfm?id=3148330}{{ACM GROUP Doctoral Consortium Travel Grant} }(\$1,000) \\

& \footnotesize{2017} & \href{http://gradorg.syr.edu/}{{Syracuse University Graduate Student Organization Travel Grant} }(\$900) \\

& \footnotesize{2017} & \href{http://www.sigchi.org/news/sigchi-sponsors-students-to-attend-turing-award-celebration}{{ACM 50th Celebration of the Turing Award Student Scholarship} }(\$900) \\

& \footnotesize{2016} & \href{http://www.sigchi.org/conferences/funding/student-travel-grant}{{ACM SIGCHI Student Travel Grant} }(\$1,500) \\

& \footnotesize{2016} & \href{https://ischool.syr.edu/research/grants-and-awards/}{{Syracuse University iSchool Doctoral Travel Grant}} (\$800) \\

& \footnotesize{2015} & \href{http://cups.cs.cmu.edu/soups/2015/cfp.php}{{Symposium on Usable Privacy and Security Travel Grant}} (\$500) \\

& \footnotesize{2015} & \href{https://ischool.syr.edu/research/grants-and-awards/}{{Syracuse University iSchool Doctoral Travel Grant}} (\$700) \\

\textcolor{black}{\footnotesize{\uppercase{Fellowships}}} & \footnotesize{2018} & \href{https://forum2018.diglib.org/fellowship-opportunities/fellows/}{{Digital Library Federation New Professional Fellowship }}(\$1,000) \\

& \footnotesize{2016} & \href{http://www.sis.pitt.edu/i3/phd-fellows/fellow-profiles.html}{{iSchool Inclusion Institute Teaching Fellowship}} (\$1,000) \\

& \footnotesize{2016} & \href{https://www.bankofamerica.com/philanthropic/foundation.go?fnId=31}{{Lloyd G. Balfour Foundation Fellowship}} (\$1,000) \\

& \footnotesize{2015} & \href{https://news.syr.edu/2015/07/ischool-student-awarded-5000-mortar-board-fellowship-22021/}{{Mortar Board Graduate Fellowship}} (\$5,000) \\

& \footnotesize{2015} & \href{https://news.syr.edu/2012/04/ischool-advisersu-trustee-creates-new-summer-ph-d-fellowships/}{{Dean’s Fellowship}} (\$7,000) \\

& \footnotesize{2013} & \href{https://www.google.com/policyfellowship/2013fellows.html}{{Google Policy Fellowship}} (\$7,500) \\

& \footnotesize{2013} & \href{https://www.syracuse.edu/admissions/cost-and-aid/types-of-aid/graduate-student-aid/fellowships/}{{Ronald E. McNair Graduate Fellowship}} (\$23,135) \\

& \footnotesize{2009} & \href{http://www.washington.edu/carlson/ellis-civic-fellowship/}{{Robert Lee Ellis Civic Fellowship}} (\$12,000) \\


\textcolor{black}{\footnotesize{\uppercase{Honors}}} & \footnotesize{2019} & \href{https://twitter.com/bdosono/status/1082439167512961024}{{Association for Information Systems, Hawaii International Conference on System Sciences Doctoral Fellow}} \\

& \footnotesize{2013} & \href{https://ischool.uw.edu/feature-stories/2013-ischool-convocation-celebrates-achievement-and-community}{{UW Faculty Award for Student Excellence in Informatics}} \\

& \footnotesize{2013} & \href{http://www.washington.edu/omad/celebration/recognition-scholarship-recipients/2013-celebration-scholarship-recipients/}{{UW President’s Achievement Award}} \\

& \footnotesize{2011} & \href{https://www.pbk.org/}{{Phi Beta Kappa}} \\

\textcolor{black}{\footnotesize{\uppercase{Scholarships}}} & \footnotesize{2013} & \href{https://expo.uw.edu/public/offering/271}{{Bill and Melinda Gates Foundation Research Scholarship}} (\$4,000) \\

& \footnotesize{2012} & \href{http://depts.washington.edu/eip/}{{Early Identification Program Presidential Scholarship}} (\$3,500) \\

& \footnotesize{2012} & \href{http://www.nsf.gov/crssprgm/reu/}{{National Science Foundation Research Experience for Undergraduates Grant}} (\$6,399) \\

& \footnotesize{2011} & \href{https://ischool.uw.edu/news/2012/04/bryan-dosono-informatics-student-speaks-boeing-scholarship-breakfast}{{Boeing Diversity Scholarship}} (\$3,000) \\

& \footnotesize{2010} & \href{http://depts.washington.edu/uwhonors/news/brief/?id=61}{{Benjamin A. Gilman International Scholarship}} (\$3,000) \\

& \footnotesize{2010} & \href{http://www2.ed.gov/programs/smart/index.html}{{National Science and Math Access to Retain Talent Grant}} (\$1,333) \\

& \footnotesize{2008} & \href{http://www.wsac.wa.gov/}{{Washington Scholar Full Tuition Scholarship}} (\$30,000) \\

& \footnotesize{2008} & \href{https://www.dellscholars.org/}{{Dell Scholars Foundation Scholarship}} (\$20,000) \\

\end{longtable}}
\end{document}}